Refinements for Open Automata

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
TODOS

There are not a lot of works that study refinement for open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
\cite{GayH:2005,BravettiZ:2021}. This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\Ludo{more and lesss than what???} internal choices and less external choices. The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.
Alternating simulation  is originating from the game theory \cite{deAlfaro:2003}, it allows  the study of relation between individual components by viewing them as alternating transition systems. In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions). However, the composition of such automata may
lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one. The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together. Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition\LUDO{we should explain that we are optimistic, then}. 
For the composability, we use the notion of comparability of holes \LUDO{do we? where?} (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.

>>>>

There are not a lot of works that study refinement for open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
\cite{GayH:2005,BravettiZ:2021}. This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\LUDO{more and lesss than what???} internal choices and less external choices. The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.
Alternating simulation  is originating from the game theory \cite{deAlfaro:2003}, it allows  the study of relation between individual components by viewing them as alternating transition systems. In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions). However, the composition of such automata may
lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one. The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together. Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition\LUDO{we should explain that we are optimistic, then}. 
For the composability, we use the notion of comparability of holes \LUDO{do we? where?} (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
